### 2017-09-26 TF-vldb2018/sec-appendix.tex

\vspace{-2ex}
Given an instance of the minimum cut problem,
we construct an instance of $h$-fragmentation problem.
It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.}

@@

\warn{The proposition is correct as when $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.}
\identifyaffball identifies \affballsx who already match with each fragment of $P$;
Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
there must exist an update in $\Delta P$ on $P_{fi}$,
such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.

>>>>

\vspace{-1ex}
An instance of the minimum cut problem is given an undirected graph $H=(V_{H},E_{H})$ and a positive integer $m$,
to find a set $S \subseteq E_{H}$ of edges whose removal leaves two disjoint connected components, with $|S|\leq m$.

\vspace{-1ex}
Given an instance of the minimum cut problem,
we construct an instance of $h$-fragmentation problem.
It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.}

@@

The proposition is correct as when $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
\identifyaffball identifies \affballsx who already match with each fragment of $P$;
Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
there must exist an update in $\Delta P$ on $P_{fi}$,
such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.

### 2017-09-26 TF-vldb2018/sec-dynamicTopk.tex

Intuitively, we want (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.
Thus we define the {\em pattern fragmentation} problem. Given $P$ and a positive integer $h$, it is to find
an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized.
\revise{The bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size
	while minimizing the cut size between pattern fragments.}

@@

\vspace{0.5ex}
The problem is intractable, as shown below.

>>>>

\vspace{0.8ex}
\revise{During the incremental process, we typically want} (1) to avoid skewed updates by balancing the sizes of all fragments and (2) to minimize the efforts to assemble the partial matches of all fragments.
Thus we define the {\em pattern fragmentation} problem. Given $P$ and a positive integer $h$, it is to find
an $h$-fragmentation of $P$ such that both $\max(|P_{fi}|)$ ($i\in[1,h]$) and $|C|$ are minimized. 
\revise{Intuitively, the bi-criteria optimization problem partitions a pattern into $h$ components of roughly equal size
	while minimizing the cut size between pattern fragments.}

@@

The problem is intractable, as shown below.

### 2017-09-26 TF-vldb2018/sec-intro.tex

\revise{
\stab (2) We develop a \warn{quadruplicate} batch algorithm with two optimization techniques for computing top-$k$ teams via team simulation.} 
We also study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching (Section~\ref{sec-tsimAlg}).
We develop a unified approach to handling the need for both pattern and data updates.
We first prove that the dynamic top-$k$ team formation problem is unbounded even for single pattern or data updates, by extending the notion of incremental boundedness~\cite{Reps96}.
In light of this, we then propose an incremental strategy based on {\em pattern fragmentation} and {\em affected balls} to localize the effects of pattern and data updates (Sections~\ref{sec-dynamictopk}). 
We finally develop a unified incremental algorithm for dealing with separate and simultaneous pattern and data updates,
with an optimization technique with the {\em early return} property for incremental top-$k$ algorithms, an analogy of the traditional early termination property (Sections~\ref{sec-IncAlg}).

>>>>

\revise{
\stab (2) We develop a batch algorithm with two optimization techniques for computing top-$k$ teams via team simulation.} 
We also study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching (Section~\ref{sec-tsimAlg}).
We develop a unified approach to handling the need for both pattern and data updates.
We first prove that the dynamic top-$k$ team formation problem is unbounded even for single pattern or data updates, by extending the notion of incremental boundedness~\cite{Reps96}.
In light of this, we then propose an incremental strategy based on {\em pattern fragmentation} and {\em affected balls} to localize the effects of pattern and data updates (Sections~\ref{sec-dynamictopk}). 
We finally develop a unified incremental algorithm for dealing with separate and simultaneous pattern and data updates,
with an optimization technique with the {\em early return} property for incremental top-$k$ algorithms, an analogy of the traditional early termination property (Sections~\ref{sec-IncAlg}).

### 2017-09-26 TF-vldb2018/sec-tsimAlg.tex

\revise{
We devise a \warn{quadruplicate} time algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for strong simulation~\cite{MaCFHW14}.}

@@

\revise{
\stitle{Incremental computing for radius varied balls}. Recall that given $G$, $P$, $k$ and $r$, \teamF\,is to find top-$k$ teams within balls $\ball{[v, t]}$, where $v \in V$ and $t \in [1,r]$.
%centered at each node in $G$ with radius $t$ varying from 1 to $r$.
However, it is extremely costly to construct all such balls, \ie $r|V|$ balls, to compute perfect subgraphs residing in them. 
Instead, \grouprec only constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$ 
where $v \in V$ and radius is $r$ , 
and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$ who shares the same center node. The correctness of \grouprec is assured by the theorem below.

>>>>

\revise{
We devise an algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for strong simulation~\cite{MaCFHW14}.}

@@

\revise{
\stitle{Incremental computing for radius varied balls}. Recall that given $G$, $P$, $k$ and $r$, \teamF\,is to find top-$k$ teams within balls $\ball{[v, t]}$, where $v \in V$ and $t \in [1,r]$.
%centered at each node in $G$ with radius $t$ varying from 1 to $r$.
However, it is extremely costly to construct all such balls, \ie $r\cdot|V|$ balls, to compute perfect subgraphs residing in them. 
Instead, \grouprec only constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$ 
where $v \in V$ and radius is $r$ , 
and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$ who shares the same center node. The correctness of \grouprec is assured by the theorem below.
